\documentclass[12pt]{extarticle}
\usepackage{fontspec}
\usepackage{graphicx}
\usepackage{alltt}
\usepackage[xetex, bookmarks, colorlinks, breaklinks]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue} 
\usepackage[usenames,dvipsnames]{color}
\setmainfont{Fontin}
\pagestyle{empty}

\newcommand{\cmr}{\fontencoding{T1}\fontfamily{cmr}\selectfont} % Computer Modern Roman

\begin{document}



{\fontsize{20}{20} \sc \noindent Luca Matteis}\\

{\cmr \noindent I'm passionate about the Semantic Web and interfaces that autonomosly shape from RDF structures. Specifically I'm interested in technologies that enable information from different sources to be easily combined such as Linked Data. I work for a future where data can be seamlessly connected to other data, enabling the creation of a distributed multidisciplinary database.}

\vspace{10 mm}

{\fontsize{15}{15} \sc \noindent Projects}

{\cmr
\begin{itemize}
  \item[] \href{http://lmatteis.github.io/ldstatic/}{LDstatic} -- Linked Data that can be hosted on GitHub Pages.
  \item[] \href{http://lmatteis.github.io/void-graph/}{VoID graph} -- Linked Data cloud in your browser using JavaScript and SVG.
\end{itemize}
}

\vspace{5 mm}

{\fontsize{15}{15} \sc \noindent Research}

{\cmr
\begin{itemize}
  \item[] \href{http://scholar.google.com/citations?user=4shOPsgAAAAJ}{Google Scholar}  
\end{itemize}
}
\vspace{5 mm}

{\fontsize{10}{10} \sc \noindent Data publishing}\\

{\cmr
Partitioning strategies for publishing queryable Linked Data.

Alternative ways of publishing Linked Data that don't require complex configurations.

User Interfaces autonomously generated by underlying RDF structures.

Better incentive mechanisms for publishing high-quality Linked Data.

Splitting and distributing datasets across various servers.

Better integration of Web APIs and Linked Data.

Linked Data availability through URIs hosted by third-parties.

}

\end{document}